### 2021-01-16 priority-gv.tex
Rewrote PCP section.

\subsubsection*{Typing}
\todo{This is a type-and-effect system and should probably be presented as such, as in [37].}
\Cref{fig:pgv-typing} gives the typing rules for PGV.
Typing rules for terms are at the top of \cref{fig:pgv-typing}. Terms are typed by a judgement $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$ stating that ``a term $\tm{M}$ has type $\ty{T}$ and an upper bound on its priority $\cs{p}$ under the typing environment $\ty{\Gamma}$''. Typing for the linear $\lambda$-calculus is standard. Linearity is ensured by splitting environments on branching rules, requiring that the environment in the variable rule consists of just the variable, and the environment in the constant and unit rules are empty. Constants $\tm{K}$ are typed using type schemas, and embedded using \LabTirName{T-Const} (mid of \cref{fig:pgv-typing}). The typing rules treat \emph{all variables} as linear resources, even those of non-linear types such as $\ty{\tyunit}$. However, the rules can easily be extended to allow values with unrestricted usage~\cite{wadler14}.

@@

We must show that substitution preserves priority constraints. For this, we prove~\cref{lem:pgv-value-done}, which shows that values have finished all their communication, and that any priorities in the type of the value come from the typing environment.
\begin{compacttheorems}
  \begin{restatablelemma}{lempgvvaluedone}
    \label{lem:pgv-value-done}
    If $\tseq[\cs{p}]{\ty{\Gamma}}{V}{T}$, then $\cs{p}=\cs{\pbot}$, and $\minpr(\ty{\Gamma})=\minpr(\ty{T})$.
  \end{restatablelemma}
  \begin{restatablelemma}{lempgvsubstitution}[Substitution]
    \label{lem:pgv-substitution}
    \hfill\\%newline before theorem statement
    If $\tseq[\cs{p}]{\ty{\Gamma},\tmty{x}{U'}}{M}{T}$ and $\tseq[\cs{q}]{\ty{\Theta}}{V}{U'}$, then $\tseq[\cs{p}]{\ty{\Gamma},\ty{\Theta}}{\subst{M}{V}{x}}{T}$.
  \end{restatablelemma}
  \begin{restatablelemma}{lempgvsubjectreductionterms}[Subject Reduction, $\tred$]
    \label{lem:pgv-subject-reduction-terms}
    \hfill\\%newline before theorem statement
    If $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$ and $\tm{M}\tred\tm{M'}$,
    then $\tseq[\cs{p}]{\ty{\Gamma}}{M'}{T}$.
  \end{restatablelemma}
  \begin{restatablelemma}{lempgvsubjectcongruence}[Subject Congruence, $\equiv$]
    \label{lem:pgv-subject-congruence}
    \hfill\\%newline before theorem statement
    If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$ and $\tm{\conf{C}}\equiv\tm{\conf{C'}}$,
    then $\cseq[\phi]{\ty{\Gamma}}{\conf{C'}}$.
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpgvsubjectreductionconfs}[Subject Reduction, $\cred$]
    \label{thm:pgv-subject-reduction-confs}
    \hfill\\%newline before theorem statement
    If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$ and $\tm{\conf{C}}\cred\tm{\conf{C'}}$,
    then $\cseq[\phi]{\ty{\Gamma}}{\conf{C'}}$.
  \end{restatabletheorem}
\end{compacttheorems}
The proofs are standard inductions. The details can be found in \cref{prf:lem-pgv-value-done,prf:lem-pgv-substitution,prf:lem-pgv-subject-reduction-terms,prf:lem-pgv-subject-congruence,prf:thm-pgv-subject-reduction-confs}.

>>>>

\subsubsection*{Typing}
\Cref{fig:pgv-typing} gives the typing rules for PGV.
Typing rules for terms are at the top of \cref{fig:pgv-typing}. Terms are typed by a judgement $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$ stating that ``a term $\tm{M}$ has type $\ty{T}$ and an upper bound on its priority $\cs{p}$ under the typing environment $\ty{\Gamma}$''. Typing for the linear $\lambda$-calculus is standard. Linearity is ensured by splitting environments on branching rules, requiring that the environment in the variable rule consists of just the variable, and the environment in the constant and unit rules are empty. Constants $\tm{K}$ are typed using type schemas, and embedded using \LabTirName{T-Const} (mid of \cref{fig:pgv-typing}). The typing rules treat \emph{all variables} as linear resources, even those of non-linear types such as $\ty{\tyunit}$. However, the rules can easily be extended to allow values with unrestricted usage~\cite{wadler14}.

@@

We must show that substitution preserves priority constraints. For this, we prove~\cref{lem:pgv-value-done}, which shows that values have finished all their communication, and that any priorities in the type of the value come from the typing environment. The proofs are standard inductions and can be found in \cref{prf:lem-pgv-value-done,prf:lem-pgv-substitution,prf:lem-pgv-subject-reduction-terms,prf:lem-pgv-subject-congruence,prf:thm-pgv-subject-reduction-confs}.
\begin{compacttheorems}
  \begin{restatablelemma}{lempgvvaluedone}
    \label{lem:pgv-value-done}
    If $\tseq[\cs{p}]{\ty{\Gamma}}{V}{T}$, then $\cs{p}=\cs{\pbot}$, and $\minpr(\ty{\Gamma})=\minpr(\ty{T})$.
  \end{restatablelemma}
  \begin{restatablelemma}{lempgvsubstitution}[Substitution]
    \label{lem:pgv-substitution}
    \hfill\\%newline before theorem statement
    If $\tseq[\cs{p}]{\ty{\Gamma},\tmty{x}{U'}}{M}{T}$ and $\tseq[\cs{q}]{\ty{\Theta}}{V}{U'}$, then $\tseq[\cs{p}]{\ty{\Gamma},\ty{\Theta}}{\subst{M}{V}{x}}{T}$.
  \end{restatablelemma}
  \begin{restatablelemma}{lempgvsubjectreductionterms}[Subject Reduction, $\tred$]
    \label{lem:pgv-subject-reduction-terms}
    \hfill\\%newline before theorem statement
    If $\tseq[\cs{p}]{\ty{\Gamma}}{M}{T}$ and $\tm{M}\tred\tm{M'}$,
    then $\tseq[\cs{p}]{\ty{\Gamma}}{M'}{T}$.
  \end{restatablelemma}
  \begin{restatablelemma}{lempgvsubjectcongruence}[Subject Congruence, $\equiv$]
    \label{lem:pgv-subject-congruence}
    \hfill\\%newline before theorem statement
    If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$ and $\tm{\conf{C}}\equiv\tm{\conf{C'}}$,
    then $\cseq[\phi]{\ty{\Gamma}}{\conf{C'}}$.
  \end{restatablelemma}
  \begin{restatabletheorem}{thmpgvsubjectreductionconfs}[Subject Reduction, $\cred$]
    \label{thm:pgv-subject-reduction-confs}
    \hfill\\%newline before theorem statement
    If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$ and $\tm{\conf{C}}\cred\tm{\conf{C'}}$,
    then $\cseq[\phi]{\ty{\Gamma}}{\conf{C'}}$.
  \end{restatabletheorem}
\end{compacttheorems}
